---
title: "Callout Paper Output"
author: "J.D. Raffa"
date: "Sept 5, 2018"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 8
    fig_width: 10
---


Just to review:

- We decided to only use MICU patients.
- Patients had to link to Census data, which eliminated some of the older ICU stays (pre 2005, and others).
- Excluded 2012 patients, as the quality is suspect.
- Hour of Callout, Hour of Discharge, and Discharge Delay are all related in a somewhat complex fashion.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
d.nonphi <- read.csv("../callout.csv")
nrow(d.nonphi)
# Please note, this file is not available for extraction from the "regular"-MIMIC III, hence the "phi"
d.phi <- read.csv("../callout-phi.csv") 
nrow(d.phi)
names(d.phi) <- tolower(names(d.phi))

library(dplyr);library(Hmisc); library(car)
library(ggplot2)
```


```{r}
d.phi %>% full_join(d.nonphi,by="icustay_id") %>% nrow()
d.phi %>% inner_join(d.nonphi,by="icustay_id") %>% nrow()
d.phi %>% full_join(d.nonphi,by="icustay_id") %>% filter(micu==1 | msicu==1) %>% nrow()
d.phi %>% inner_join(d.nonphi,by="icustay_id") %>% filter(micu==1 | msicu==1) %>% nrow()

d <- d.phi %>% full_join(d.nonphi,by="icustay_id") %>% filter(micu==1 | msicu==1)
d$HOSP_FREE_DAYS <- (28 - d$los_post_icu_days)*(d$los_post_icu_days<28)*(1-d$hospitaldeath)
d$CALLOUT_DURING_ROUNDS <- d$hourofcallout>700 & d$hourofcallout<1200;
d$CALLOUT_DURING_NIGHT <- d$hourofcallout>2300 | d$hourofcallout<700;
d$DISCHARGEDELAY_HOURS <- d$dischargedelay_days*24;
d$hourofcallout2 <- floor(d$hourofcallout/100) + ((d$hourofcallout/100) - floor(d$hourofcallout/100))*100/60
d <- d %>% filter(callout_year<2012 & callout_year>2001)
nrow(d)
d$PROPFULL_BEDS <- rowSums(d[,grep("census",names(d))],na.rm=TRUE)/rowSums(d[,grep("beds",names(d))],na.rm=TRUE)
#d <- d %>% mutate(ethnicity=stringr::str_sub(ethnicity,0,20))
d <- d %>% mutate(ethnicity=recode_factor(ethnicity,`WHITE`="White",
                                           `WHITE - EASTERN EUROPEAN`="White",
                                           `WHITE - RUSSIAN` = "White",
                                           `WHITE - BRAZILIAN` = "White",
                                           `WHITE - OTHER EUROPEAN` = "White",
                                           `BLACK/AFRICAN AMERICAN` = "African American/Black",
                                           `BLACK/CAPE VERDEAN`= "African American/Black",
                                           `BLACK/HAITIAN`= "African American/Black",
                                           `BLACK/AFRICAN` = "African American/Black",
                                           .default="Other"),MED_SERVICE=service=="MED")
```


Below are the Overall patient characteristics.

```{r}
library(MASS);library(splines);library(mgcv);library(plotly)
d$discharge_time <- d$hourofcallout2 + d$DISCHARGEDELAY_HOURS
d$discharge_time <- ifelse(d$discharge_time<24, d$discharge_time,d$discharge_time - floor(d$discharge_time/24)*24)
d$daypostcall <- floor((d$hourofcallout2 + d$DISCHARGEDELAY_HOURS)/24)
d$postcalldaycat2 <- cut2(d$daypostcall,c(1))

library(tableone)
vars1 <- c("micu","age", "callout_month","female","request_tele","request_resp","request_cdiff","request_mrsa", "request_vre","oasis","elixhauser_hospital","ethnicity","MED_SERVICE","HOSP_FREE_DAYS","callout_dayofweek","CALLOUT_DURING_NIGHT","CALLOUT_DURING_ROUNDS","DISCHARGEDELAY_HOURS","hourofcallout2","PROPFULL_BEDS","postcalldaycat2","hospitaldeath","los_preicu_days","los_post_callout_days","los_post_icu_days","los_pre_callout_days", "callout_year")
factorVars1 = c("micu", "female","ethnicity","MED_SERVICE", "callout_month", "request_tele","request_resp","request_cdiff","request_mrsa", "request_vre","service","callout_dayofweek","CALLOUT_DURING_ROUNDS","CALLOUT_DURING_NIGHT","postcalldaycat2","hospitaldeath","callout_year")
nonnormal.vars = c("los_preicu_days","los_post_callout_days","los_post_icu_days","los_pre_callout_days", "hourofcallout2","HOSP_FREE_DAYS")


CreateTableOne(data=d,vars=vars1,factorVars = factorVars1) %>% print(
  printToggle      = FALSE,
  showAllLevels    = TRUE,
  cramVars         = "kon",nonnormal = nonnormal.vars
) %>%
{data.frame(
  variable_name             = gsub(" ", "&nbsp;", rownames(.), fixed = TRUE), ., 
  row.names        = NULL, 
  check.names      = FALSE, 
  stringsAsFactors = FALSE)} %>% 
knitr::kable(caption="Patient Characteristics Overall") 
```


# Question 1: Who has long discharge delays?


```{r}
CreateTableOne(data=d %>% mutate(DisDelay=cut2(DISCHARGEDELAY_HOURS,c(0,4,8,24))),vars=vars1,factorVars = factorVars1,strata="DisDelay",test=TRUE) %>% print(
  printToggle      = FALSE,
  showAllLevels    = TRUE,
  cramVars         = "kon",nonnormal = nonnormal.vars
) %>%
{data.frame(
  variable_name             = gsub(" ", "&nbsp;", rownames(.), fixed = TRUE), ., 
  row.names        = NULL, 
  check.names      = FALSE, 
  stringsAsFactors = FALSE)} %>% 
knitr::kable(caption="Patient Characteristics By Discharge Delay Categories (Hours)") 


```

Determinants of the DD are quite complex, depending on many factors.  We instead focus on breaking down DD to >=24 vs <24h



```{r}
CreateTableOne(data=d %>% mutate(DisDelay=cut2(DISCHARGEDELAY_HOURS,c(24))),vars=vars1,factorVars = factorVars1,strata="DisDelay",test=TRUE) %>% print(
  printToggle      = FALSE,
  showAllLevels    = TRUE,
  cramVars         = "kon",nonnormal = nonnormal.vars
) %>%
{data.frame(
  variable_name             = gsub(" ", "&nbsp;", rownames(.), fixed = TRUE), ., 
  row.names        = NULL, 
  check.names      = FALSE, 
  stringsAsFactors = FALSE)} %>% 
knitr::kable(caption="Patient Characteristics By Discharge Delay Categories (Hours)") 


```

We fit a logistic regression model for DD>24 as the "outcome" with:

1. Demographics: age, sex, 
2. Requests: tele, resp, mrsa, cdiff, vre
3. Adjustment for severity/comoribidity/icu los: oasis, exlixhauser, los_pre_callout_days
4. Possible structural/admin variables: DOW, month, year.
5. Census variables: type of bed requested, proportion of hospital beds is use.

as covariates.

Model selection: fit full model, reduce backwards stepwise, until all variables are significant by LRT.

AIC/BIC model selection was done first, but used only as a comparison to the manually worked selection (`jdr.ddelay.glm`).

```{r}

library(sjPlot)


full.model.glm <- glm(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]" ~ cut2(oasis,g=3) + cut2(age,g=3) + female + request_tele + request_resp + request_mrsa + request_vre + request_cdiff + cut2(elixhauser_hospital,g=3) + cut2(los_pre_callout_days,c(1,3,7,28)) + as.factor(callout_month) + as.factor(callout_year) + as.factor(callout_dayofweek) + as.factor(callout_wardid==1)*cut2(PROPFULL_BEDS,c(0.9,1)) + MED_SERVICE + cut2(hourofcallout2,c(7,12,19)),data=d,family="binomial" )

drop1(full.model.glm,test="Chisq")
sjPlot::plot_model(full.model.glm,Title="Full Model, ddelay")

library(MASS)
final.model.glm.bic <- stepAIC(full.model.glm,k=log(nobs(full.model.glm)),trace=0)
sjPlot::plot_model(final.model.glm.bic,Title="BIC Model, ddelay")
drop1(final.model.glm.bic,test="Chisq")

final.model.glm.aic <- stepAIC(full.model.glm,trace=0)
sjPlot::plot_model(final.model.glm.aic,Title="AIC Model, ddelay")
drop1(final.model.glm.aic,test="Chisq")



full.model.glm <- glm(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]" ~ cut2(oasis,g=3) + cut2(age,g=3) + female + request_tele + request_resp + request_mrsa + request_vre + request_cdiff + cut2(elixhauser_hospital,g=3) + cut2(los_pre_callout_days,c(1,3,7,28)) + as.factor(callout_month) + as.factor(callout_year) + as.factor(callout_dayofweek) + as.factor(callout_wardid==1)*cut2(PROPFULL_BEDS,c(0.9,1)) + MED_SERVICE + relevel(cut2(hourofcallout2,c(7,12,19)),"[ 7.000,12.000)"),data=d,family="binomial" )

#1

drop.res <- drop1(full.model.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[which.max(drop.res$`Pr(>Chi)`)]
drop.res$`Pr(>Chi)`[which.max(drop.res$`Pr(>Chi)`)]


#2 
jdr.ddelay.glm <- update( full.model.glm, .~. - cut2(age, g = 3))
drop.res <- drop1(jdr.ddelay.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[which.max(drop.res$`Pr(>Chi)`)]
drop.res$`Pr(>Chi)`[which.max(drop.res$`Pr(>Chi)`)]

#3

jdr.ddelay.glm <- update( jdr.ddelay.glm, .~. - cut2(elixhauser_hospital, g = 3))
drop.res <- drop1(jdr.ddelay.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[which.max(drop.res$`Pr(>Chi)`)]
drop.res$`Pr(>Chi)`[which.max(drop.res$`Pr(>Chi)`)]

#4

jdr.ddelay.glm <- update( jdr.ddelay.glm, .~. - MED_SERVICE)
drop.res <- drop1(jdr.ddelay.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[which.max(drop.res$`Pr(>Chi)`)]
drop.res$`Pr(>Chi)`[which.max(drop.res$`Pr(>Chi)`)]

#5

jdr.ddelay.glm <- update( jdr.ddelay.glm, .~. - request_resp)
drop.res <- drop1(jdr.ddelay.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[which.max(drop.res$`Pr(>Chi)`)]
drop.res$`Pr(>Chi)`[which.max(drop.res$`Pr(>Chi)`)]

#6

jdr.ddelay.glm <- update( jdr.ddelay.glm, .~. - request_tele)
drop.res <- drop1(jdr.ddelay.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[which.max(drop.res$`Pr(>Chi)`)]
drop.res$`Pr(>Chi)`[which.max(drop.res$`Pr(>Chi)`)]

#7 

jdr.ddelay.glm <- update( jdr.ddelay.glm, .~. - cut2(oasis, g = 3))
drop.res <- drop1(jdr.ddelay.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[which.max(drop.res$`Pr(>Chi)`)]
drop.res$`Pr(>Chi)`[which.max(drop.res$`Pr(>Chi)`)]

#8

jdr.ddelay.glm <- update( jdr.ddelay.glm, .~. - cut2(los_pre_callout_days, c(1, 3, 7, 28)))
drop.res <- drop1(jdr.ddelay.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[which.max(drop.res$`Pr(>Chi)`)]
drop.res$`Pr(>Chi)`[which.max(drop.res$`Pr(>Chi)`)]

#stop

summary(jdr.ddelay.glm)
sjt.glm(jdr.ddelay.glm)
plot_model(jdr.ddelay.glm)

# leave outs:
leave.out <- c(1,35,36)
out <- round(cbind(exp(jdr.ddelay.glm$coef)[-leave.out],exp(confint(jdr.ddelay.glm)[-leave.out,]),summary(jdr.ddelay.glm)$coef[-leave.out,4]),3)

#interactions: using Wald intervals/tests
covM <- summary(jdr.ddelay.glm)$cov.unscale[c(30:31,35:36),c(30:31,35:36)]
Z <- matrix(c(1,0,0,1,1,0,0,1),nr=2);
se <- sqrt(diag(Z%*%covM%*%t(Z)))
out <- rbind(out,round(cbind(exp(jdr.ddelay.glm$coef[30:31] +jdr.ddelay.glm$coef[35:36]),exp(jdr.ddelay.glm$coef[30:31] +jdr.ddelay.glm$coef[35:36] - qnorm(0.975)*se), exp(jdr.ddelay.glm$coef[30:31] +jdr.ddelay.glm$coef[35:36] + qnorm(0.975*se)),pnorm(-(jdr.ddelay.glm$coef[30:31] +jdr.ddelay.glm$coef[35:36])/se)*2),3))
write.csv(file="out-table-ddelay.csv",out)  # CSV was used in the paper, after formatting, rounding, etc.

```

## Answer 1: 

**Solid evidence**: When Hospital is near or over capacity, when mrsa/cdiff have to be taken into account (more likely); When the callout is made during rounds or in more recent calendar year (less likely).

**Less Solid Evidence**: All of the above **PLUS**: On certain days of the week, sicker patients (OASIS), certain months, vre (more likely); Female (less likely).  Effect modified of "first available bed" and propfull beds. E.g., when hospital is <90% used: "first available bed" => less likely to have a long delay, but effect is negated or reversed when hospitals are full.


# Question 2: Do people who have long discharge delays (>24 hours) die more often?


- Marginal evidence in above table: 5.4% vs 6.8% (p=0.06), but we know these patients are generally sicker, more likely to have concerns about cdiff, vre, mrsa, etc.


We will build a model in a similar way as before, but add the long discharge delay (>24hrs) into a model for hospital mortality, retaining our exposure of interested (DD) throughout.
```{r}
vars1 <- c("micu","age", "callout_month","female","request_tele","request_resp","request_cdiff","request_mrsa", "request_vre","oasis","elixhauser_hospital","ethnicity","MED_SERVICE","HOSP_FREE_DAYS","callout_dayofweek","CALLOUT_DURING_NIGHT","CALLOUT_DURING_ROUNDS","DISCHARGEDELAY_HOURS","hourofcallout2","PROPFULL_BEDS","postcalldaycat2","los_preicu_days","los_post_callout_days","los_post_icu_days","los_pre_callout_days", "callout_year")
factorVars1 = c("micu", "female","ethnicity","MED_SERVICE", "callout_month", "request_tele","request_resp","request_cdiff","request_mrsa", "request_vre","service","callout_dayofweek","CALLOUT_DURING_ROUNDS","CALLOUT_DURING_NIGHT","postcalldaycat2","callout_year")
nonnormal.vars = c("los_preicu_days","los_post_callout_days","los_post_icu_days","los_pre_callout_days", "hourofcallout2","HOSP_FREE_DAYS")


CreateTableOne(data=d,vars=vars1,factorVars = factorVars1,strata="hospitaldeath") %>% print(
  printToggle      = FALSE,
  showAllLevels    = TRUE,
  cramVars         = "kon",nonnormal = nonnormal.vars
) %>%
{data.frame(
  variable_name             = gsub(" ", "&nbsp;", rownames(.), fixed = TRUE), ., 
  row.names        = NULL, 
  check.names      = FALSE, 
  stringsAsFactors = FALSE)} %>% 
knitr::kable(caption="Patient Characteristics Overall") 

```

```{r}
full.model.glm <- glm(hospitaldeath ~ I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]") +cut2(oasis,g=3) + cut2(age,g=3) + female + request_tele + request_resp + request_mrsa + request_vre + request_cdiff + cut2(elixhauser_hospital,g=3) + cut2(los_pre_callout_days,c(1,3,7,28)) + as.factor(callout_month) + as.factor(callout_year) + as.factor(callout_dayofweek) + as.factor(callout_wardid==1)*cut2(PROPFULL_BEDS,c(0.9,1)) + MED_SERVICE + relevel(cut2(hourofcallout2,c(7,12,19)),"[ 7.000,12.000)"),data=d,family="binomial" )

drop1(full.model.glm,test="Chisq")
sjPlot::plot_model(full.model.glm,Title="Full Model, mortality")

library(MASS)
final.model.glm.bic <- stepAIC(full.model.glm,k=log(nobs(full.model.glm)),trace=0,scope=list(lower=~I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")))
sjPlot::plot_model(final.model.glm.bic,Title="BIC Model, mortality")
drop1(final.model.glm.bic,test="Chisq")

final.model.glm.aic <- stepAIC(full.model.glm,trace=0,scope=list(lower=~I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")))
sjPlot::plot_model(final.model.glm.aic,Title="AIC Model, mortality")
drop1(final.model.glm.aic,test="Chisq")


#jdr
full.model.glm <- glm(hospitaldeath ~ I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]") +cut2(oasis,g=3) + cut2(age,g=3) + female + request_tele + request_resp + request_mrsa + request_vre + request_cdiff + cut2(elixhauser_hospital,g=3) + cut2(los_pre_callout_days,c(1,3,7,28)) + as.factor(callout_month) + as.factor(callout_year) + as.factor(callout_dayofweek) + as.factor(callout_wardid==1)*cut2(PROPFULL_BEDS,c(0.9,1)) + MED_SERVICE + relevel(cut2(hourofcallout2,c(7,12,19)),"[ 7.000,12.000)"),data=d,family="binomial" )
summary(full.model.glm)
drop1(full.model.glm)

#1



drop.res <- drop1(full.model.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#2 
jdr.death.glm <- update( full.model.glm, .~. - request_resp)
drop.res <- drop1(jdr.death.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#3 
jdr.death.glm <- update( jdr.death.glm, .~. - request_mrsa)
drop.res <- drop1(jdr.death.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#interaction almost same as age!
#4
jdr.death.glm <- update( jdr.death.glm, .~. - as.factor(callout_wardid == 1):cut2(PROPFULL_BEDS, c(0.9, 1)))
drop.res <- drop1(jdr.death.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#5 

jdr.death.glm <- update( jdr.death.glm, .~. - cut2(PROPFULL_BEDS, c(0.9, 1)))
drop.res <- drop1(jdr.death.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#6

jdr.death.glm <- update( jdr.death.glm, .~. - cut2(age, g = 3))
drop.res <- drop1(jdr.death.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#7 

jdr.death.glm <- update( jdr.death.glm, .~. - as.factor(callout_dayofweek))
drop.res <- drop1(jdr.death.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#8 

jdr.death.glm <- update( jdr.death.glm, .~. - as.factor(callout_month))
drop.res <- drop1(jdr.death.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#9 

jdr.death.glm <- update( jdr.death.glm, .~. - MED_SERVICE)
drop.res <- drop1(jdr.death.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#10 

jdr.death.glm <- update( jdr.death.glm, .~. - relevel(cut2(hourofcallout2, c(7, 12, 19)), "[ 7.000,12.000)"))
drop.res <- drop1(jdr.death.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#11 

jdr.death.glm <- update( jdr.death.glm, .~. - female)
drop.res <- drop1(jdr.death.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


plot_model(jdr.death.glm)
sjt.glm(jdr.death.glm)

leave.out <- 1
out2 <- round(cbind(exp(jdr.death.glm$coef)[-leave.out],exp(confint(jdr.death.glm)[-leave.out,]),summary(jdr.death.glm)$coef[-leave.out,4]),3)
print(out2)
write.csv(file="out-table-death.csv",out2)


```

## Answer 2: After adjusting for potential confounders, there is no statistically significant evidence that a long delay produces a better hospital mortality outcome.


# Question 3:  Do individuals with a long discharge delay have smaller numbers of hospital free days?

HFDs are technically ordinal, so we tried Proportional Odds Logistic Regression.  This didn't make it into the paper.

There is not very much evidence in the above table that hospital free days is impacted by long discharge delays (21.36 vs 21.09, p=0.265)

We can look at it using an empirical cumulative distribution function:
```{r}

spl <- split(d,cut2(d$DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")
plot(ecdf(floor(spl[[1]]$HOSP_FREE_DAYS)),main="ecdf red=short delay",lwd=2)
lines(ecdf(floor(spl[[2]]$HOSP_FREE_DAYS)),col="red")

```



# Question 4: Do people who have long discharge delays (>24 hours) have a "good outcome" defined as a short post discharge LOS (<1 week) and survive?

```{r}
with(d,table(HOSP_FREE_DAYS>21))
with(d,table(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]"))
with(d,table(HOSP_FREE_DAYS>21,cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]"))

prop.table(with(d,table(HOSP_FREE_DAYS>21,cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")),2)
chisq.test(with(d,table(HOSP_FREE_DAYS>21,cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")))

vars1 <- c("micu","age", "callout_month","female","request_tele","request_resp","request_cdiff","request_mrsa", "request_vre","oasis","elixhauser_hospital","ethnicity","MED_SERVICE","HOSP_FREE_DAYS","callout_dayofweek","CALLOUT_DURING_NIGHT","CALLOUT_DURING_ROUNDS","DISCHARGEDELAY_HOURS","hourofcallout2","PROPFULL_BEDS","postcalldaycat2","los_preicu_days","los_post_callout_days","los_post_icu_days","los_pre_callout_days", "callout_year","hospitaldeath")
factorVars1 = c("micu", "female","ethnicity","MED_SERVICE", "callout_month", "request_tele","request_resp","request_cdiff","request_mrsa", "request_vre","service","callout_dayofweek","CALLOUT_DURING_ROUNDS","CALLOUT_DURING_NIGHT","postcalldaycat2","callout_year")
nonnormal.vars = c("los_preicu_days","los_post_callout_days","los_post_icu_days","los_pre_callout_days", "hourofcallout2")

d$GOOD_HFDs <- d$HOSP_FREE_DAYS>21;
CreateTableOne(data=d,vars=vars1,factorVars = factorVars1,strata="GOOD_HFDs") %>% print(
  printToggle      = FALSE,
  showAllLevels    = TRUE,
  cramVars         = "kon",nonnormal = nonnormal.vars
) %>%
{data.frame(
  variable_name             = gsub(" ", "&nbsp;", rownames(.), fixed = TRUE), ., 
  row.names        = NULL, 
  check.names      = FALSE, 
  stringsAsFactors = FALSE)} %>% 
knitr::kable(caption="Patient Characteristics Overall") 

```



```{r}
full.model.glm <- glm(I(HOSP_FREE_DAYS>21) ~ I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]") +cut2(oasis,g=3) + cut2(age,g=3) + female + request_tele + request_resp + request_mrsa + request_vre + request_cdiff + cut2(elixhauser_hospital,g=3) + cut2(los_pre_callout_days,c(1,3,7,28)) + as.factor(callout_month) + as.factor(callout_year) + as.factor(callout_dayofweek) + as.factor(callout_wardid==1)*cut2(PROPFULL_BEDS,c(0.9,1)) + MED_SERVICE + relevel(cut2(hourofcallout2,c(7,12,19)),"[ 7.000,12.000)"),data=d,family="binomial" )

drop1(full.model.glm,test="Chisq")
sjPlot::plot_model(full.model.glm,Title="Full Model, mortality")

library(MASS)
final.model.glm.bic <- stepAIC(full.model.glm,k=log(nobs(full.model.glm)),trace=0,scope=list(lower=~I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")))
sjPlot::plot_model(final.model.glm.bic,Title="BIC Model, mortality")
drop1(final.model.glm.bic,test="Chisq")

final.model.glm.aic <- stepAIC(full.model.glm,trace=0,scope=list(lower=~I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")))
sjPlot::plot_model(final.model.glm.aic,Title="AIC Model, mortality")
drop1(final.model.glm.aic,test="Chisq")

#jdr
full.model.glm <- glm(I(HOSP_FREE_DAYS>21) ~ I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]") +cut2(oasis,g=3) + cut2(age,g=3) + female + request_tele + request_resp + request_mrsa + request_vre + request_cdiff + cut2(elixhauser_hospital,g=3) + cut2(los_pre_callout_days,c(1,3,7,28)) + as.factor(callout_month) + as.factor(callout_year) + as.factor(callout_dayofweek) + as.factor(callout_wardid==1)*cut2(PROPFULL_BEDS,c(0.9,1)) + MED_SERVICE + relevel(cut2(hourofcallout2,c(7,12,19)),"[ 7.000,12.000)"),data=d,family="binomial" )
summary(full.model.glm)
drop1(full.model.glm)

#1



drop.res <- drop1(full.model.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#2 
jdr.goodhfd.glm <- update( full.model.glm, .~. - as.factor(callout_wardid == 1):cut2(PROPFULL_BEDS, c(0.9, 1)))
drop.res <- drop1(jdr.goodhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#3
jdr.goodhfd.glm <- update( jdr.goodhfd.glm, .~. - MED_SERVICE)
drop.res <- drop1(jdr.goodhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#4
jdr.goodhfd.glm <- update( jdr.goodhfd.glm, .~. - request_tele)
drop.res <- drop1(jdr.goodhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#5
jdr.goodhfd.glm <- update( jdr.goodhfd.glm, .~. - as.factor(callout_dayofweek))
drop.res <- drop1(jdr.goodhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#6
jdr.goodhfd.glm <- update( jdr.goodhfd.glm, .~. -cut2(PROPFULL_BEDS, c(0.9, 1)))
drop.res <- drop1(jdr.goodhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#7
jdr.goodhfd.glm <- update( jdr.goodhfd.glm, .~. -female)
drop.res <- drop1(jdr.goodhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#8
jdr.goodhfd.glm <- update( jdr.goodhfd.glm, .~. -as.factor(callout_month))
drop.res <- drop1(jdr.goodhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#9
jdr.goodhfd.glm <- update( jdr.goodhfd.glm, .~. -relevel(cut2(hourofcallout2, c(7, 12, 19)), "[ 7.000,12.000)"))
drop.res <- drop1(jdr.goodhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#10
jdr.goodhfd.glm <- update( jdr.goodhfd.glm, .~. -request_mrsa)
drop.res <- drop1(jdr.goodhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#11
jdr.goodhfd.glm <- update( jdr.goodhfd.glm, .~. -request_resp)
drop.res <- drop1(jdr.goodhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

plot_model(jdr.goodhfd.glm)
sjt.glm(jdr.goodhfd.glm)

leave.out <- 1
out3 <- round(cbind(exp(jdr.goodhfd.glm$coef)[-leave.out],exp(confint(jdr.goodhfd.glm)[-leave.out,]),summary(jdr.goodhfd.glm)$coef[-leave.out,4]),3)
print(out3)
write.csv(file="out-table-good_hfd.csv",out3)


```

## Answer 4: After adjusting for potential confounders, there is no statistically significant evidence that a long delay produces a better HFD outcome (>21 days).


# Question 5: Do people who have long discharge delays (>24 hours) have a "bad outcome" defined as a long post discharge LOS (>3 week) or death?

```{r}
with(d,table(HOSP_FREE_DAYS<=7))
with(d,table(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]"))
with(d,table(HOSP_FREE_DAYS<=7,cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]"))

prop.table(with(d,table(HOSP_FREE_DAYS<=7,cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")),2)
chisq.test(with(d,table(HOSP_FREE_DAYS<=7,cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")))
```


```{r}
vars1 <- c("micu","age", "callout_month","female","request_tele","request_resp","request_cdiff","request_mrsa", "request_vre","oasis","elixhauser_hospital","ethnicity","MED_SERVICE","HOSP_FREE_DAYS","callout_dayofweek","CALLOUT_DURING_NIGHT","CALLOUT_DURING_ROUNDS","DISCHARGEDELAY_HOURS","hourofcallout2","PROPFULL_BEDS","postcalldaycat2","los_preicu_days","los_post_callout_days","los_post_icu_days","los_pre_callout_days", "callout_year","hospitaldeath")
factorVars1 = c("micu", "female","ethnicity","MED_SERVICE", "callout_month", "request_tele","request_resp","request_cdiff","request_mrsa", "request_vre","service","callout_dayofweek","CALLOUT_DURING_ROUNDS","CALLOUT_DURING_NIGHT","postcalldaycat2","callout_year")
nonnormal.vars = c("los_preicu_days","los_post_callout_days","los_post_icu_days","los_pre_callout_days", "hourofcallout2")

d$BAD_HFDs <- d$HOSP_FREE_DAYS<=7;
CreateTableOne(data=d,vars=vars1,factorVars = factorVars1,strata="BAD_HFDs") %>% print(
  printToggle      = FALSE,
  showAllLevels    = TRUE,
  cramVars         = "kon",nonnormal = nonnormal.vars
) %>%
{data.frame(
  variable_name             = gsub(" ", "&nbsp;", rownames(.), fixed = TRUE), ., 
  row.names        = NULL, 
  check.names      = FALSE, 
  stringsAsFactors = FALSE)} %>% 
knitr::kable(caption="Patient Characteristics Overall") 

```


```{r}
full.model.glm <- glm(I(HOSP_FREE_DAYS<=7) ~ I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]") +cut2(oasis,g=3) + cut2(age,g=3) + female + request_tele + request_resp + request_mrsa + request_vre + request_cdiff + cut2(elixhauser_hospital,g=3) + cut2(los_pre_callout_days,c(1,3,7,28)) + as.factor(callout_month) + as.factor(callout_year) + as.factor(callout_dayofweek) + as.factor(callout_wardid==1)*cut2(PROPFULL_BEDS,c(0.9,1)) + MED_SERVICE + relevel(cut2(hourofcallout2,c(7,12,19)),"[ 7.000,12.000)"),data=d,family="binomial" )

drop1(full.model.glm,test="Chisq")
sjPlot::plot_model(full.model.glm,Title="Full Model, mortality")

 library(MASS)
final.model.glm.bic <- stepAIC(full.model.glm,k=log(nobs(full.model.glm)),trace=0,scope=list(lower=~I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")))
sjPlot::plot_model(final.model.glm.bic,Title="BIC Model, mortality")
drop1(final.model.glm.bic,test="Chisq")

final.model.glm.aic <- stepAIC(full.model.glm,trace=0,scope=list(lower=~I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")))
sjPlot::plot_model(final.model.glm.aic,Title="AIC Model, mortality")
drop1(final.model.glm.aic,test="Chisq")


#jdr
full.model.glm <- glm(I(HOSP_FREE_DAYS<=7) ~ I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]") +cut2(oasis,g=3) + cut2(age,g=3) + female + request_tele + request_resp + request_mrsa + request_vre + request_cdiff + cut2(elixhauser_hospital,g=3) + cut2(los_pre_callout_days,c(1,3,7,28)) + as.factor(callout_month) + as.factor(callout_year) + as.factor(callout_dayofweek) + as.factor(callout_wardid==1)*cut2(PROPFULL_BEDS,c(0.9,1)) + MED_SERVICE + relevel(cut2(hourofcallout2,c(7,12,19)),"[ 7.000,12.000)"),data=d,family="binomial" )
summary(full.model.glm)
drop1(full.model.glm)

#1



drop.res <- drop1(full.model.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#2 
jdr.badhfd.glm <- update( full.model.glm, .~. - request_mrsa)
drop.res <- drop1(jdr.badhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#3
jdr.badhfd.glm <- update( jdr.badhfd.glm, .~. - as.factor(callout_dayofweek))
drop.res <- drop1(jdr.badhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#4
jdr.badhfd.glm <- update( jdr.badhfd.glm, .~. - as.factor(callout_wardid == 1):cut2(PROPFULL_BEDS, c(0.9, 1)))
drop.res <- drop1(jdr.badhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#5
jdr.badhfd.glm <- update( jdr.badhfd.glm, .~. - cut2(PROPFULL_BEDS, c(0.9, 1)))
drop.res <- drop1(jdr.badhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#6
jdr.badhfd.glm <- update( jdr.badhfd.glm, .~. - as.factor(callout_month))
drop.res <- drop1(jdr.badhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#7
jdr.badhfd.glm <- update( jdr.badhfd.glm, .~. - request_resp)
drop.res <- drop1(jdr.badhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#8
jdr.badhfd.glm <- update( jdr.badhfd.glm, .~. - MED_SERVICE)
drop.res <- drop1(jdr.badhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#9
jdr.badhfd.glm <- update( jdr.badhfd.glm, .~. - female)
drop.res <- drop1(jdr.badhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]



#10
jdr.badhfd.glm <- update( jdr.badhfd.glm, .~. - relevel(cut2(hourofcallout2, c(7, 12, 19)), "[ 7.000,12.000)"))
drop.res <- drop1(jdr.badhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#11
jdr.badhfd.glm <- update( jdr.badhfd.glm, .~. - cut2(age, g = 3))
drop.res <- drop1(jdr.badhfd.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


plot_model(jdr.badhfd.glm)
sjt.glm(jdr.badhfd.glm)

leave.out <- 1
out4 <- round(cbind(exp(jdr.badhfd.glm$coef)[-leave.out],exp(confint(jdr.badhfd.glm)[-leave.out,]),summary(jdr.badhfd.glm)$coef[-leave.out,4]),3)
print(out4)
write.csv(file="out-table-bad_hfd.csv",out4)

```

## Answer 5: After adjusting for potential confounders, there is no statistically significant evidence that a long delay yield lower rates of poor HFD outcome (<7 days).


# Question 6: Do survivors of the hospital stay who have long discharge delays have longer log(LOS_post_icu)?

Post ICU days were similar in the above table 5.95 vs 6.19 (p=0.35)





```{r}
full.model.glm <- lm(log(los_post_icu_days + 1) ~  I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]") +cut2(oasis,g=3) + cut2(age,g=3) + female + request_tele + request_resp + request_mrsa + request_vre + request_cdiff + cut2(elixhauser_hospital,g=3) + cut2(los_pre_callout_days,c(1,3,7,28)) + as.factor(callout_month) + as.factor(callout_year) + as.factor(callout_dayofweek) + as.factor(callout_wardid==1)*cut2(PROPFULL_BEDS,c(0.9,1)) + MED_SERVICE + relevel(cut2(hourofcallout2,c(7,12,19)),"[ 7.00,12.00)"),data=(d %>% filter(hospitaldeath==0)) )

drop1(full.model.glm,test="F")
sjPlot::plot_model(full.model.glm,Title="Full Model, LOS")

library(MASS)
final.model.glm.bic <- stepAIC(full.model.glm,k=log(nobs(full.model.glm)),trace=0,scope=list(lower=~I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")))
sjPlot::plot_model(final.model.glm.bic,Title="BIC Model, LOS")
drop1(final.model.glm.bic,test="F")

final.model.glm.aic <- stepAIC(full.model.glm,trace=0,scope=list(lower=~I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]")))
sjPlot::plot_model(final.model.glm.aic,Title="AIC Model, LOS")
drop1(final.model.glm.aic,test="F")


#jdr
full.model.glm <- lm(log(los_post_icu_days + 1) ~  I(cut2(DISCHARGEDELAY_HOURS,c(24))=="[ 24.000,129.566]") +cut2(oasis,g=3) + cut2(age,g=3) + female + request_tele + request_resp + request_mrsa + request_vre + request_cdiff + cut2(elixhauser_hospital,g=3) + cut2(los_pre_callout_days,c(1,3,7,28)) + as.factor(callout_month) + as.factor(callout_year) + as.factor(callout_dayofweek) + as.factor(callout_wardid==1)*cut2(PROPFULL_BEDS,c(0.9,1)) + MED_SERVICE + relevel(cut2(hourofcallout2,c(7,12,19)),"[ 7.00,12.00)"),data=(d %>% filter(hospitaldeath==0)) )
summary(full.model.glm)
drop1(full.model.glm)

#1



drop.res <- drop1(full.model.glm ,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#2 
jdr.los.glm <- update( full.model.glm, .~. - as.factor(callout_wardid == 1):cut2(PROPFULL_BEDS, c(0.9, 1)))
drop.res <- drop1(jdr.los.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#3
jdr.los.glm <- update( jdr.los.glm, .~. -as.factor(callout_month))
drop.res <- drop1(jdr.los.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


#4 


jdr.los.glm <- update( jdr.los.glm, .~. -as.factor(callout_year))
drop.res <- drop1(jdr.los.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]

#5

jdr.los.glm <- update( jdr.los.glm, .~. -relevel(cut2(hourofcallout2, c(7, 12, 19)), "[ 7.00,12.00)"))
drop.res <- drop1(jdr.los.glm,test="Chisq")
print(drop.res)
rownames(drop.res)[-2][which.max(drop.res$`Pr(>Chi)`[-2])]
drop.res$`Pr(>Chi)`[-2][which.max(drop.res$`Pr(>Chi)`[-2])]


plot_model(jdr.los.glm)
sjt.glm(jdr.los.glm)

leave.out <- 1
out5 <- round(cbind((jdr.los.glm$coef)[-leave.out],(confint(jdr.los.glm)[-leave.out,]),summary(jdr.los.glm)$coef[-leave.out,4]),3)
print(out5)
write.csv(file="out-table-los.csv",out5)


#plot(jdr.los.glm)


```

## Answer 6: After adjusting for potential confounders, There appears to be some evidence that those with long delays have about 12\% shorter post ICU LOS.


